---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/poissonconsulting/timer.svg?branch=master)](https://travis-ci.org/poissonconsulting/timer)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/timer?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/timer)
[![codecov](https://codecov.io/gh/poissonconsulting/timer/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/timer)

# timer

## Introduction

An R package implementing a simple timer as an R6 class.

The timer has four functions: `$start()`, `$stop()`, `$reset()` and `$elapsed()`.
The `$elapsed()` function returns the elapsed wall clock time (as opposed to CPU time)
as an object of class `lubridate::Duration`.

## Utilisation

```{r}
library(timer)

# instantiate a new timer
timer <- Timer$new()

# no time has elapsed because the timer has not started
timer$elapsed()

# start the timer
timer$start()

# get the time elapsed (as an object of class lubridate::Duration)
# time elapsed is increasing because the timer is still running
timer$elapsed()
timer$elapsed()

# stop the timer
timer$stop()

# time elapsed is now fixed
timer$elapsed()
timer$elapsed()

# because timer is an object of class R6 use the clone() function
# to make a copy
timer2 <- timer$clone()

# reset the timer
timer$reset()
timer$elapsed()

# timer2 is not reset
timer2$elapsed()
```

## Installation

To install from GitHub
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/timer")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/timer/issues).

[Pull requests](https://github.com/poissonconsulting/timer/pulls) are always welcome.

## Documentation

- [Introduction to R6 classes](https://cran.r-project.org/package=R6/vignettes/Introduction.html).
